MinCall --- MinION end2end deep learning basecaller

### 2017-07-01 paper/main.tex
Rewritten Acknowledgments
* Added Sigopt
* Added NVIDIA Corporation for GPU donations
* Removed co-authors from acknowledgment section

During testing, we tried ReLu and PrELU~\cite{prelu} with no significant result difference. We also tried different channel numbers, receptive field width, and various other hyperparameters during hyperparameter optimization and conclude after enough complexity, that is sufficient layers, all choices were performing similarly.

@@

\section{Acknowledgments}
First and foremost I'd like to thank my mentor izv.~prof.~dr.~sc.~Mile Šikić for setting up the problem, guiding us through its beginnings and providing helpful advice for its completion. Next Marko Ratković for his not only insightful conversations but also meaningful code contributions.

Finally, I'm thanking various other people whose code, tools and advice I've used in completing this paper: Fran Jurišić, Ana Marija Selak, Ivan Sović, Robert Vaser and Martin Šošić.

Also, some data were obtained in cooperation with Biologists doc.~dr.~sc. Petra Korać and dr.sc. Paula Dobrinić. Other were procured publicly shared from Loman labs~\cite{loman1-100k}

>>>>

During testing, we tried ReLu and PrELU~\cite{prelu} with no significant result difference. We also tried different channel numbers, receptive field width, and various other hyperparameters during hyperparameter optimization and conclude after enough complexity, that is sufficient layers, all choices were performing similarly. We used SigOpt~\cite{dewancker2016strategy}\footnote{\url{https://sigopt.com/}} bayesian hyperoptimization library.

@@

\section{Acknowledgments}

During this paper creation we used Sigopt academic licence for hyperparameter optimization. We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Titan Xp GPU used for this research.

We're thankful to various other people whose code, tools and advice we've used in completing this project: Fran Jurišić, Ana Marija Selak, Ivan Sović, Robert Vaser and Martin Šošić.

For data, we're thankful for cooperation of Biologists doc.~dr.~sc. Petra Korać and dr.sc. Paula Dobrinić and Loman labs~\cite{loman1-100k} for publicly posting their dataset.
